\documentclass[10pt, a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{changepage}
\usepackage[shortlabels]{enumitem}
\usepackage{microtype, xspace}
\usepackage{hyperref}
\newcommand{\hmargin}{2.5cm}
\geometry{top=2.0cm,
    bottom=2.0cm,
    left=\hmargin,
    right=\hmargin}
\hypersetup{colorlinks=true, linkcolor=cyan, urlcolor=cyan}
\pagenumbering{gobble}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlist{topsep=0pt, itemsep=0pt}

% Footer configuration
%--------------------------------------------%
\usepackage{fancyhdr, extramarks}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C]{\small \textit{Source code available at \textup{\href{https://github.com/DeanGadberry/cv}{\texttt{github.com/DeanGadberry/cv}}} under the \textup{CC BY-NC-SA 4.0} license.}}
% \renewcommand{\sectionmark}[1]{
%     \markboth{\thesection. \ #1}
%     {\noexpand\firstsubsectiontitle}
%     \global\firstsubsectionmarktrue}
% \renewcommand{\subsectionmark}[1]{
%     \markright{\thesubsection. \, #1}
%     \iffirstsubsectionmark
% \edef\firstsubsectiontitle{\thesubsection. \, #1}
% \fi
% \global\firstsubsectionmarkfalse}
% \newif\iffirstsubsectionmark
% \def\firstsubsectiontitle{}
\setlength{\headheight}{14pt} 
%--------------------------------------------%
% End footer configuration

% BEGIN CUSTOM MACROS
% --------------------------------------------- %
\newcommand{\rangesep}{to\xspace}  % for date ranges
\renewcommand{\date}[1]{\textit{#1}}
\newcommand{\location}[1]{\textit{#1}}
\newcommand{\contentType}[1]{\textit{#1}}
\newcommand{\heading}[1]{
    \makebox[0pt][l]{\Large \sc \hspace{2pt}#1}
    \rule[-0.7ex]{\columnwidth}{0.5pt}\vspace{1.0ex}
}
\newcommand{\subheading}[1]{{\bfseries #1}}
\newcommand{\generalInfoSkip}{\vspace{0.3ex}}
\newcommand{\subheadSkip}{\vspace{0.7ex}}
\newcommand{\contentIndent}{\hspace{1em}}
% --------------------------------------------- %
% END CUSTOM MACROS

% BEGIN CUSTOM ENVIRONMENTS
% --------------------------------------------- %
\newenvironment{mysection}[1]
{\vspace{2.5ex}
\heading{#1}
\begin{adjustwidth}{0.3cm}{0cm}}
{\end{adjustwidth} }
\newenvironment{entry}
\par
{\vspace{0.1ex}}
{}
% --------------------------------------------- %
% END CUSTOM ENVIRONMENTS

\begin{document}
    \textbf{\LARGE Dean Gadberry}

    \vspace{1.5ex}
    Webpage: \href{https://www.deangadberry.com}{\texttt{www.DeanGadberry.com}}\\
    GitHub: \href{https://github.com/deangadberry}{\texttt{www.github.com/DeanGadberry}}\\
    Email: \href{mailto:dean@deangadberry.com}{\texttt{Dean@DeanGadberry.com}}\\
    Phone: \href{tel:14694200771}{\texttt{469-420-0771}}

    \begin{mysection}{Summary}
%        \textbf{Citizenship:} United States 

%        \generalInfoSkip
%        \textbf{Fluent languages:} English

%        \generalInfoSkip
        \textbf{Skills include:} 
        Relationship-based team management;
        Therapeutic client management; 
        Teaching primitive survival skills;
        Tutoring introductory through undergraduate mathematics, computer programming, linux, chemistry, and biology;
        Front-end web development; 
        Website database design;
        Technical Writing;
        {\LaTeX};
        Adobe Acrobat; 
        Microsoft Office 365;
        Unix core utilities;
        Working on a \texttt{systemd} Linux system;
        Git and GitHub.
    \end{mysection} 

%    \begin{mysection}{Portfolio}
%        \subheading{Web-Based Manufacturing Process Tracking} \hfill \contentType{Website Database Development}
%        \begin{entry}
%            \hspace{1em} Full-Stack AWS-hosted ERP-style software, built for Classy Closets of DFW using Django.
%        \end{entry}
%    \end{mysection}

    \begin{mysection}{Education}
        \subheading{North Central Texas College} \hfill \location{Corinth, TX, USA}

        \textit{Computer Science transfer to UNT} \hfill \date{present}

        \subheadSkip
        \subheading{UofN School of Biblical Studies} \hfill \location{Kansas City, USA}

        \textit{Certificate in Inductive Biblical Studies} \hfill \date{2021}

%        \vspace{0.1ex}
%        \begin{entry}
%            \hspace{1em} Charts of significant Biblical Events and Possible Interpretations

%            \hspace{1em} Charts webpage: \url{https://www.DeanGadberry.com/sbs}
%        \end{entry}
            
        \subheadSkip
        \subheading{UofN School of Missions} \hfill \location{Dubai, UAE; Beirut, Lebanon}

        \textit{Certificate in Cross-Cultural Missions} \hfill \date{2020}

        \subheadSkip
        \subheading{UofN Discipleship Training School} \hfill \location{Newcastle, Australia; Gorkha, Nepal}

        \textit{Certificate III in Discipleship} \hfill \date{2019}

%        \subheadSkip
%        \subheading{Heritage Schools} \hfill \location{Provo, Utah, USA}
%
%        \textit{High School Diploma} \hfill \date{2016}
%
%        \subheadSkip
%        \subheading{Millikan High School} \hfill \location{Long Beach, CA, USA}
%
%        \textit{High School} \hfill \date{August 2012 \rangesep July 2015}
    \end{mysection}

    \begin{mysection}{Employment}
        \subheading{Classy Closets of DFW} \hfill \location{Grapevine, TX, USA}

        \textit{Accounts Payable/Receivable \& Payroll; Closet Installer } \hfill \date{April 2022 \rangesep present}

        \vspace{0.1ex}
%        Classy Closets is a custom closet company which designs, manufactures and installs closets.

%        Webpage: \url{https://www.classyclosets.com}

        \begin{itemize}
            \item Conduct full cycle Accounts Payable/Receivable function with QuickBooks. General Ledger account coding; Payments to vendors; Monthly Accounting Reconciliation.
            \item Check Deposits 
            \item Weekly Payroll 
            \item Pay company taxes through EFTPS.
            \item Write standard operating procedures.
            \item Develop Manufacturing Process Tracking software.
        \end{itemize}

        \subheadSkip
        \subheading{North Central Texas College} \hfill \location{Flower Mound, TX, USA}

        \vspace{0.1ex}
        \textit{Math \& Science Tutor} \hfill \date{January 2023 \rangesep present}
        \begin{itemize}
            \item Provide one-on-one tutoring college sessions to students in math and science courses, such as algebra, chemistry, and biology.
            \item Assist students with homework, test preparation, and understanding mathematical concepts.
            \item Provide one-on-one tutoring sessions to students in computer-related courses, such as Computer Programming Fundamentals, and Introduction to Linux 
        \end{itemize}

        \subheadSkip
        \subheading{Amazon Fulfillment Center} \hfill \location{Columbia, SC, USA}

        \vspace{0.1ex}
        \textit{Warehouse Inbound Indirect Team Lead} \hfill \date{January 2022 \rangesep March 2022}
        \begin{itemize}
            \item Receive and distribute inbound merchandise. 
            \item Interdepartmental Communication.
            \item Orchestrate dynamic warehouse layout.
        \end{itemize}

        \subheadSkip
        \subheading{MESA Mexican Cuisine} \hfill \location{Grapevine, TX, USA}

        \textit{Manager On Duty; Bartender; Server} \hfill \date{July 2018 \rangesep July 2020}

        \begin{itemize}
            \item Manage nightly operations to efficiently meet customer service demands and promote store profitability. Supervise restaurant staff. Final preparation of outgoing food.
            \item Mix and serve drink.
            \item Provide table side customer service.
        \end{itemize}
    \end{mysection}

    \newpage
    \begin{mysection}{Employment \large{(continued)}}

        \subheadSkip
        \subheading{Wingate Wilderness Therapy} \hfill \location{Grand Staircase-Escalante, UT, USA}

        \vspace{0.1ex}
        \textit{Field Instructor} \hfill \date{March 2017 \rangesep April 2018}
        \begin{itemize}
            \item Care for at-risk youth in a therapeutic environment. Fascilitate conflict resolution between clients. 
            \item Prepare weekly reports about client interactions and significant events. 
            \item Administer prescription and over-the-counter medications to minors and adults, including controlled substances.
            \item Leading a group as a cross-country backpacking guide, without established trails. Navigate using traditional methods with a map and compass.
            \item Teach primitive skills: Ancient fire-making techniques; Creation of leather shoes, bags, and primitive backpacks; Identification of edible and dangerous plants; Use of natural resources for survival.
        \end{itemize}

        \subheadSkip
        \subheading{ACE Hardware} \hfill \location{Long Beach, CA, USA}

        \vspace{0.1ex}
        \textit{Retail Staff} \hfill \date{September 2014 \rangesep January 2015}
        \begin{itemize}
            \item Operate point-of-sale software for customer payment.
            \item Provide direct customer service at checkout. 
            \item Advise customers on product selection and use.
            \item Present merchandise to customers in an intuitive manner using vertical merchandising techniques.
            \item Organize and restock shelves.
        \end{itemize}
    \end{mysection} 

\end{document}
